White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-11-14 papers/wdmerger_II/paper.tex
Move the problem setup to be section 2

@@

%==========================================================================
% Problem Setup
%==========================================================================
\section{Problem Setup}
\label{sec:problemsetup}

We terminate the simulation at $t = 9$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring.

>>>>

%==========================================================================
% Problem Setup
%==========================================================================
\section{White Dwarf Collisions}
\label{sec:collisions}

We start with a description of the problem setup and results of a typical collision
at low resolution. These results set the stage for our numerical methodology. This enables
a concrete discussion about the methodology using the language of how it affects the
collision outcome. In this setting, a concrete discussion is more fruitful than an abstract one.

\subsection{Problem Setup}
\label{sec:problemsetup}

We terminate the simulation at $t = 9$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring. In our discussions below, it helps to have some other
anchoring points in time when significant events occur. We (arbitrarily) define the
collision time, $t_c$, as the first time when the maximum density on the grid reaches
$5 \times 10^6\ \text{g / cm}^3$. This is slightly larger than the initial maximum
density of the two WDs, and is reached only when the WDs meet at the center of the
domain. We define the detonation time, $t_d$, as the time when the temperature
first reaches $5 \times 10^9\ \text{K}$.

\subsection{Baseline Results}
\label{sec:baseline_results}

Now let us examine the results for a collision of two 0.64 $\msolar$ WDs. We use
128 zones in the radial dimension, corresponding to a spatial resolution of 312.5 km.
Timesteps are limited only by the hydrodynamic stability constraint (and the plotfile
interval constraint). Resolutions in the range of a few hundred km have been a common
choice in earlier papers on white dwarf mergers and collisions. No adaptive mesh
refinement is used. For this configuration, the collision time is $t_c = 6.47\ \text{s}$,
and the detonation time is $t_d = 7.43\ \text{s}$. The peak density at the detonation time
is $2.3 \times 10^7\ \text{g / cm}^3$.

@@
